Conditional selectivity for Hexastores

### 2011-07-20 conditional/trunk/selectivity-hexastore.tex
correct left-hand
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@9 43ef1190-90fd-4dd7-a769-d0121f02b80e
Improve TODO command
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@10 43ef1190-90fd-4dd7-a769-d0121f02b80e
RDF node -> RDF term
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@13 43ef1190-90fd-4dd7-a769-d0121f02b80e

\newcommand{\rdfnode}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\tiny{TODO}\normalsize\footnote{\textbf{TODO:}~#1}}

@@

\begin{abstract}
In this paper we see how the common assumption of independence of the
selectivity of RDF nodes can be abandoned. We shall also find it
instructive to explore how selectivity can be determined exactly when
a SPARQL query is executed on a Hexastore triple store
\cite{Weiss:2008:HSI:1453856.1453965}. Finally, we will suggest
further directions for selectivity estimation in the conditional
regime.

@@

The above authors assume that the selectivity of RDF nodes are
independent, admit that this assumption is easily violated and
continue to use a conditional estimate for the object node.

@@

Previous authors have taken selectivity as analogous to the
probability of matching a SPARQL node\todo{terminology, (SPARQL nodes
  vs. RDF nodes) could be better} or triple with a node or triple
in the data. For a triple, $<S, P, O>$ the selectivity is the
intersection of the selectivity of each node.

@@

Finally, note that for unbound nodes (variables), the selectivity will
always be unity, whether conditional or independent, since it will
match all possible RDF nodes.

@@

Then, 
\begin{equation}
sel(S) = \frac{cm(s_i)}{i} ,
\end{equation}
\begin{equation}
sel(P) = \frac{cm(p_{n_i}^i)}{n_i}
\end{equation}
and
\begin{equation}
sel(O) = \frac{cm(o_{k_{i,n_i}}^{i,n_i})}{k_{i,n_i}}
\end{equation}

>>>>

\newcommand{\rdfnode}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

@@

\begin{abstract}
In this paper we see how the common assumption of independence of the
selectivity of RDF terms can be abandoned. We shall also find it
instructive to explore how selectivity can be determined exactly when
a SPARQL query is executed on a Hexastore triple store
\cite{Weiss:2008:HSI:1453856.1453965}. Finally, we will suggest
further directions for selectivity estimation in the conditional
regime.

@@

The above authors assume that the selectivity of RDF terms are
independent, admit that this assumption is easily violated and
continue to use a conditional estimate for the object node.

@@

Previous authors have taken selectivity as analogous to the
probability of matching a SPARQL node\todo{terminology, (SPARQL nodes
  vs. RDF terms) could be better} or triple with a node or triple
in the data. For a triple, $<S, P, O>$ the selectivity is the
intersection of the selectivity of each node.

@@

Finally, note that for unbound nodes (variables), the selectivity will
always be unity, whether conditional or independent, since it will
match all possible RDF terms.

@@

Then, 
\begin{equation}
sel(S) = \frac{cm(s_i)}{i} ,
\end{equation}
\begin{equation}
sel(P|S) = \frac{cm(p_{n_i}^i)}{n_i}
\end{equation}
and
\begin{equation}
sel(O|S \cap P) = \frac{cm(o_{k_{i,n_i}}^{i,n_i})}{k_{i,n_i}}
\end{equation}
